Cropland percentage bias and accuracy, part II

### 2017-01-27 Rmd/c4-cropland-2.Rmd
Added output to c4-cropland-2.Rmd for area estimates with each level of aggregation for each cropland dataset.

# calculate km2 cropland in LC datasets
awgts <- lapply(area_wgts, function(x) x[[1]])
lckm2 <- do.call(rbind, lapply(1:length(lev), function(x) {  # x <- 1
  gtia <- cellStats(gti_agg[[x]]$g2011 / 100 * awgts[[x]], sum)
  lca <- sapply(snms, function(y) {
    cellStats(lc_agg[[x]][[y]] / 100 * awgts[[x]], sum)
  })
  o <- c(gtia, lca)
}))

@@

>>>>

# calculate km2 cropland in LC datasets
awgts <- lapply(area_wgts, function(x) x[[1]])
lckm2 <- do.call(rbind, lapply(1:length(lev), function(x) {  # x <- 1
  gtia <- cellStats(gti_agg[[x]]$g2011 / 100 * awgts[[x]], sum)
  lca <- sapply(snms, function(y) {
    cellStats(lc_agg[[x]][[y]] / 100 * awgts[[x]], sum)
  })
  o <- c(gtia, lca)
}))
colnames(lckm2)[1] <- "gti"
rownames(lckm2) <- lev2

@@

Cropland area by dataset and scale
```{r, echo = FALSE}
round(lckm2)
```
